DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM

### 2022-05-05 paper.tex
waiting for simulation to finish

% #############################################################################
% #############################################################################
\section{Conclusions}
\label{sec:conclusion}
In this paper, a distributed adaptive algorithm for blind system identification using ADMM in the context of sensor networks was developed.
The BSI problem is distributed amongst the nodes by exploiting the separability of the cross-relation problem formulation which leads to node-wise sub-problems using signal information of a node's neighborhood.
The nodes solve the subproblem and transmit estimates to their respective neighbors which are combined into consensus estimates,
Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms.
Further they suggest that steady-state performance is not affected by the separation of the full BSI problem into node-wise sub-problems while convergence speed is.

>>>>

% #############################################################################
% #############################################################################
\section{Conclusions}
\label{sec:conclusion}
In this paper, a distributed adaptive algorithm for blind system identification using ADMM in the context of sensor networks was developed.
The BSI problem is distributed amongst the nodes by exploiting the separability of the cross-relation problem formulation which leads to node-wise sub-problems using signal information of a node's neighborhood.
The nodes solve the subproblem and transmit estimates to their respective neighbors which are combined into consensus estimates,
Preliminary results using white Gaussian noise and randomly generated impulse responses have demonstrated improved steady-state error measures compared to state-of-the-art algorithms.
Further, they suggest that steady-state performance is not affected by the separation of the full BSI problem into node-wise sub-problems while convergence speed is.
